Our Title

### 2015-05-01 draft.tex
Changed Glossary Appendix format style.

Radioactive Decay: The spontaneous transformation of one radioisotope into one or more different isotopes. The isotopes created may or may not also be radioactive. Radioactive decay may also be used to refer to the emission of a gamma ray or a conversion electron emission, which reduces the energy of the decaying isotope but does not change its identity.

Alpha Radiation: The radioactive decay of a nuclide which results in the emission of a 4-Helium atom. Alpha radiation is sometimes followed by gamma emission.

Beta Radiation: A radioactive decay of a nuclide which results in the emission of an electron and an electron antineutrino pair, or a positron and an electron neutrino pair.

Fusion: A nuclear reaction in which atomic nuclei of low atomic number merge and become a heavier nucleus, thereby releasing energy.

Special Nuclear Material: Plutonium, 233-Uranium, Uranium with enrichments of 233-Uranium or 235-Uranium.

Gamma Radiation: A radioactive decay which results in the emission of a high energy- short-wavelength, electromagnetic radiation emitted from within the nucleus of an atom. Gamma radiation often follows the emission of an alpha or beta particle, and always follows a fission event.

Electron Volt: A unit of energy equivalent to the work required to accelerate an electron through a potential difference of 1 volt.

Fission: The splitting of an atom, which releases energy. During fission, a heavy (large A) nucleus splits into two or three smaller nuclei and emits gamma rays and neutrons.

Nuclide: A distinct nucleus, defined by the total number of neutrons and protons contained therein.

Fast Neutron: A neutron with kinetic energy in excess of 1.5 MeV.

Thermal Neutron: A neutron which is in thermal equilibrium with its surroundings.

Fissile Material: A nuclide that is capable of undergoing fission after capturing thermal neutrons.

Fissionable Material: A nuclide that is capable of undergoing fission after capturing a fast or thermal neutron.

>>>>

\textbf{Radioactive Decay:} The spontaneous transformation of one radioisotope into one or more different isotopes. The isotopes created may or may not also be radioactive. Radioactive decay may also be used to refer to the emission of a gamma ray or a conversion electron emission, which reduces the energy of the decaying isotope but does not change its identity.

\textbf{Alpha Radiation:} The radioactive decay of a nuclide which results in the emission of a 4-Helium atom. Alpha radiation is sometimes followed by gamma emission.

\textbf{Beta Radiation:} A radioactive decay of a nuclide which results in the emission of an electron and an electron antineutrino pair, or a positron and an electron neutrino pair.

\textbf{Fusion:} A nuclear reaction in which atomic nuclei of low atomic number merge and become a heavier nucleus, thereby releasing energy.

\textbf{Special Nuclear Material:} Plutonium, 233-Uranium, Uranium with enrichments of 233-Uranium or 235-Uranium.

\textbf{Gamma Radiation:} A radioactive decay which results in the emission of a high energy- short-wavelength, electromagnetic radiation emitted from within the nucleus of an atom. Gamma radiation often follows the emission of an alpha or beta particle, and always follows a fission event.

\textbf{Electron Volt:} A unit of energy equivalent to the work required to accelerate an electron through a potential difference of 1 volt.

\textbf{Fission:} The splitting of an atom, which releases energy. During fission, a heavy (large A) nucleus splits into two or three smaller nuclei and emits gamma rays and neutrons.

\textbf{Nuclide:} A distinct nucleus, defined by the total number of neutrons and protons contained therein.

\textbf{Fast Neutron:} A neutron with kinetic energy in excess of 1.5 MeV.

\textbf{Thermal Neutron:} A neutron which is in thermal equilibrium with its surroundings.

\textbf{Fissile Material:} A nuclide that is capable of undergoing fission after capturing thermal neutrons.

\textbf{Fissionable Material:} A nuclide that is capable of undergoing fission after capturing a fast or thermal neutron.
